Millions of Type Errors

### 2023-04-19 oopsla23/paper.tex
table: rows with error

\begin{figure}[t]
  %% TODO split counts, total = current + previous
  \begin{tabular}{rl}
   5,001 & total logs \\
         & 4,471 nocheck + 506 nonstrict + 24 strict \\
   182,247 & total forced strict type errors \\
         & {83,005 in module, 5,113 in edit regions} \\
    1,521 & total type errors \\
         & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
    \\[2ex]

@@

\begin{figure}[t]
  %% TODO draw bars or curves b/c numbers are too hard to compare horizontally

  TODOD table: mode (fs), project, module, region; cell olde,curr; two rows per actual mode ... or two tables

@@

  \begin{tabular}{lrrr}
    Error Label & \# Added & \# Persist & \# Remove \\\midrule
    CodeTooComplex
    & 0 & 0 & 0 \\
    UnificationTooComplex
    & 0 & 0 & 0 \\[1ex]
    SyntaxError
    & 30 & 0 & 76 \\
    UnknownSymbol
    & 12 & 14 & 19 \\
    UnknownProperty
    & 3 & 1 & 4 \\
    UnknownRequire
    & 1 & 5 & 0 \\
    GenericError
    & 1 & 0 & 1 \\
    CountMismatch
    &  1 &  0 &  1 \\
    OptionalValueAccess
    &  0 &  0 &  1 \\
  \end{tabular}

>>>>

\begin{figure}[t]
  \begin{tabular}{rl}
   5,001 & total logs \\
         & 4,471 nocheck + 506 nonstrict + 24 strict \\
         & 1,628 from module switches \\
   182,247 & total forced strict type errors \\
         & {83,005 in module, 5,113 in edit regions} \\
    1,521 & total type errors \\
         & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
    \\[2ex]

@@

\begin{figure}[t]
  %% TODO stacked bars?
  %% TODO align old;curr
  \begin{tabular}{lrrrrr}
    Mode             & \# Rows & E         & Any Error & In Module & In Region \\
      & & & & (old ; curr) &  (old ; curr) \\\midrule
    \code{nocheck}   &   4,471 & \code{te} &    5.77\% &  0.20\% ;  2.21\% &  0.16\% ;  0.63\% \\
                     &         & \code{fs} &   59.18\% & 32.81\% ; 49.16\% &  9.17\% ; 13.13\% \\
    \code{nonstrict} &     506 & \code{te} &   25.89\% & 12.06\% ; 18.18\% &  6.32\% ;  7.91\% \\
                     &         & \code{fs} &   62.45\% & 37.94\% ; 53.75\% & 16.60\% ; 20.75\% \\
    \code{strict}    &      24 & \code{te} &   50.00\% & 29.17\% ; 33.33\% &     0\% ;     0\% \\
                     &         & \code{fs} &   62.50\% & 50.00\% ; 58.33\% &  4.17\% ;  8.33\% 
  \end{tabular}

  \bigskip

@@

  %% TODO draw bars or curves b/c numbers are too hard to compare horizontally
  \begin{tabular}{lrrr}
    Error Label & \# Add & \# Keep & \# Remove \\\midrule
    CodeTooComplex
    & 0 & 0 & 0 \\
    UnificationTooComplex
    & 0 & 0 & 0 \\[1ex]
    SyntaxError
    & 30 & 0 & 76 \\
    UnknownSymbol
    & 12 & 14 & 19 \\
    UnknownProperty
    & 3 & 1 & 4 \\
    UnknownRequire
    & 1 & 5 & 0 \\
    GenericError
    & 1 & 0 & 1 \\
    CountMismatch
    &  1 &  0 &  1 \\
    OptionalValueAccess
    &  0 &  0 &  1 \\
  \end{tabular}
